---
title: "3-3-ModelRevision"
author: "Charlie Repaci"
date: "3/2/2021"
output: html_document
---

```{r, warning = FALSE, message = FALSE}
# Load any R Packages you may need
library(tidyverse)
library(mosaic)
library(moderndive)
library(ggplot2)
library(dplyr)
library(haven)
library(forcats)
library(labelled)
library(ggmosaic)
library(corrplot)
library(caret)
library(caTools)
library(leaps)
library(e1071)
library(effects)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
# Load any datasets you may need
setwd("/Users/carly/Desktop/Marquette REU/107 Factors that Influence the Decision Not to Substantiate a CPS Referral/Data/")

phasei <- read_sas("phasei_c.sas7bdat", catalog_file = "formats.sas7bcat")

dim(phasei)

names(phasei)[1:664] = tolower(names(phasei)[1:664])
phasei = to_factor(phasei)
phasei = mutate_all(phasei, na_if, "n/a")
```

```{r}
phasei$overallx = ifelse(phasei$overallr == "NO RISK" | phasei$overallr == "LOW" | phasei$overallr == "MOD LOW", 0, 1)
#tally(phasei$overallr)
#tally(phasei$overallx)

data = select(phasei, nrisk1,nrisk2,nrisk3,nrisk4,nrisk5,nrisk6,nrisk7,nrisk8,nrisk9,nrisk10,nrisk11,nrisk12,nrisk13,nrisk14,nrisk15,nrisk16,nrisk17,nrisk18,nrisk19,nrisk20,nrisk21,nrisk22,nrisk23,nrisk24,nrisk25,nrisk26,nrisk27,nrisk28,nrisk29,nrisk30,nrisk31,nrisk32,nrisk33,nrisk34,nrisk35,nrisk36,nrisk37,nrisk38,nrisk39,nrisk40,nrisk41,nrisk42,nrisk43,nrisk44,nrisk45,nrisk46,nrisk47,nrisk48,nrisk49,nrisk50,nrisk51,nrisk52,nrisk53,nrisk54,nrisk55,nrisk56,nrisk57,nrisk58,nrisk59)

dim(data)

# Credit: https://stackoverflow.com/questions/55634193/replace-strings-with-values-across-multiple-columns-at-once
data = mutate_all(data, ~case_when(. %in% "NO RISK" ~ '0', 
                   . == "LOW" ~ '1', 
                   . == "MOD LOW" ~ '2', 
                   . == "MOD" ~ '3', 
                   . == "MOD HIGH" ~ '4',
                   . == "HIGH" ~ '5', 
                   TRUE ~ NA_character_))

data$overallx = phasei$overallx

tally(phasei$nrisk1)
tally(data$nrisk1)

data = mutate_all(data, as.numeric)
data
```

***
***
***

##Explore (via regression, variance and correlation) impact of economic factors and cooperation with social workers

###Simple Regression

80/20 split on train and test data sets
Source: https://www.analytics-tuts.com/how-to-split-train-and-test-data-in-r/
```{r}
set.seed(9158)
data$overallx = as_factor(data$overallx)
tempdat = sort(sample(nrow(data), nrow(data)*.8))
train<-data[tempdat,]
test<-data[-tempdat,]
dim(train)
dim(test)

tr = select(train, !c(nrisk52,nrisk53,nrisk56,nrisk57))
te = select(test, !c(nrisk52,nrisk53,nrisk56,nrisk57))
dim(tr)
dim(te)
```

Binomial model and prediction based on all variables
```{r}
set.seed(9158)
regmod = glm(overallx~., data=train, family = binomial)
summary(regmod)
allvar = predict(regmod, test, "response")
av = ifelse(allvar>=0.5, 1, 0)
tally(test$overallx~av, format='percent')
```

Binomial model and prediction based on all variables except 52, 53, 56, 57
```{r}
set.seed(9158)
regmod2 = glm(overallx~., data=tr, family = binomial)
summary(regmod2)
allvar2 = predict(regmod2, te, "response")
av2 = ifelse(allvar2>=0.5, 1, 0)
tally(test$overallx~av2, format='percent')
```

####Backstep models

All of the variables:
```{r}
set.seed(9158)

fitall = glm(overallx~., family = binomial, data = train)
backstep = step(fitall, direction = "backward")
```

```{r}
set.seed(9158)

tenfold = trainControl(method = "cv", number = 10)

#based on the best model from the backward step:
backbest = train(overallx ~ nrisk1 + nrisk5 + nrisk6 + nrisk7 + 
    nrisk8 + nrisk14 + nrisk15 + nrisk16 + nrisk20 + nrisk22 + 
    nrisk24 + nrisk25 + nrisk26 + nrisk28 + nrisk29 + nrisk32 + 
    nrisk33 + nrisk36 + nrisk37 + nrisk41 + nrisk42 + nrisk44 + 
    nrisk45 + nrisk46 + nrisk50 + nrisk54, data = train, method = "glm", trControl = tenfold)

backbesttest = predict(backbest, test)
backpred = ifelse(backbesttest>=0.5, 1, 0)
tally(test$overallx~backpred, format='percent')

backimportance = varImp(backbest, sort=TRUE)
backimportance
plot(backimportance)

```

```{r}
backbestglm = glm(formula = overallx ~ nrisk1 + nrisk5 + nrisk6 + nrisk7 +
    nrisk8 + nrisk14 + nrisk15 + nrisk16 + nrisk20 + nrisk22 +
    nrisk24 + nrisk25 + nrisk26 + nrisk28 + nrisk29 + nrisk32 +
    nrisk33 + nrisk36 + nrisk37 + nrisk41 + nrisk42 + nrisk44 +
    nrisk45 + nrisk46 + nrisk50 + nrisk54, family = binomial,
    data = train)

summary(backbestglm)

confint(backbestglm)
exp(coef(backbestglm))

backbestglmtest = predict(backbestglm, test)
backpredglm = ifelse(backbestglmtest>=0.5, 1, 0)
tally(test$overallx~backpredglm, format='percent')


```

```{r}
plot(allEffects(backbestglm))
```

All vars except econ:
```{r}
fitecon = glm(overallx~., family = binomial, data = tr)
ebackstep = step(fitecon, direction = "backward")
ebackstepped = predict(ebackstep, te, "response")
ebk = ifelse(ebackstepped>=0.5, 1, 0)
tally(test$overallx~ebk, format='percent')
```

####ANOVA
```{r}
anova(regmod2, regmod)
anova(fitall, fitecon)
```

####Forward step
```{r}
set.seed(9158)

fitbase = glm(overallx~1, family = binomial, data = train)
forstep = step(fitbase, direction = "forward", scope = formula(fitall))
```

```{r}
set.seed(9158)
#based on the best model from the forward step:
forbest = train(overallx ~ nrisk36 + nrisk15 + nrisk50 + nrisk1 + 
    nrisk32 + nrisk54 + nrisk42 + nrisk20 + nrisk8 + nrisk26 + 
    nrisk46 + nrisk6 + nrisk14 + nrisk7 + nrisk28 + nrisk22 + 
    nrisk16, data = train, method = "glm", trControl = tenfold)

forbesttest = predict(backbest, test)
forpred = ifelse(forbesttest>=0.5, 1, 0)
tally(test$overallx~forpred, format='percent')

summary(forbest)

forimportance = varImp(forbest, sort=TRUE)
forimportance
plot(forimportance)
```


###Correlation

```{r}
# tests employment status (52, 53) and economic resources (56, 57)
econrelated = round(cor(select(data,nrisk52,nrisk53,nrisk56,nrisk57),
                        select(data,overallx,nrisk1,nrisk2,nrisk3,nrisk4,nrisk5,nrisk6,nrisk7,nrisk8,nrisk9,nrisk10,
                               nrisk11,nrisk12,nrisk13,nrisk14,nrisk15,nrisk16,nrisk17,nrisk18,nrisk19,nrisk20,
                               nrisk21,nrisk22,nrisk23,nrisk24,nrisk25,nrisk26,nrisk27,nrisk28,nrisk29,nrisk30,
                               nrisk31,nrisk32,nrisk33,nrisk34,nrisk35,nrisk36,nrisk37,nrisk38,nrisk39,nrisk40,
                               nrisk41,nrisk42,nrisk43,nrisk44,nrisk45,nrisk46,nrisk47,nrisk48,nrisk49,nrisk50,
                               nrisk51,nrisk52,nrisk53,nrisk54,nrisk55,nrisk56,nrisk57,nrisk58,nrisk59
                               ), use = 'pairwise.complete.obs'), digits = 1)
corrplot(econrelated, method="shade", type="upper")


# tests recognition of problem (32, 33) and cooperation with agency (36, 37)
cooprelated = round(cor(select(data,nrisk32,nrisk33,nrisk36,nrisk37),
                        select(data,overallx,nrisk1,nrisk2,nrisk3,nrisk4,nrisk5,nrisk6,nrisk7,nrisk8,nrisk9,nrisk10,
                               nrisk11,nrisk12,nrisk13,nrisk14,nrisk15,nrisk16,nrisk17,nrisk18,nrisk19,nrisk20,
                               nrisk21,nrisk22,nrisk23,nrisk24,nrisk25,nrisk26,nrisk27,nrisk28,nrisk29,nrisk30,
                               nrisk31,nrisk32,nrisk33,nrisk34,nrisk35,nrisk36,nrisk37,nrisk38,nrisk39,nrisk40,
                               nrisk41,nrisk42,nrisk43,nrisk44,nrisk45,nrisk46,nrisk47,nrisk48,nrisk49,nrisk50,
                               nrisk51,nrisk52,nrisk53,nrisk54,nrisk55,nrisk56,nrisk57,nrisk58,nrisk59
                               ), use = 'pairwise.complete.obs'), digits = 1)
corrplot(cooprelated, method="shade", type="upper")


# Source: https://stackoverflow.com/questions/50614105/correlated-variables-at-a-threshold
x = names(data)

c = data.frame(t(combn(x,2)), stringsAsFactors = F) %>%
  rowwise() %>%
  mutate(v = cor(data[,X1], data[,X2]))

d = filter(c, v >= .5, X2 == "nrisk52" || X2 == "nrisk53" || X2 == "nrisk56" || X2 == "nrisk57")
d

e = filter(c, v >= .5, X2 == "nrisk32" || X2 == "nrisk33" || X2 == "nrisk36" || X2 == "nrisk37")
e
```

```{r}
highrelated = round(cor(
              select(data,overallx,nrisk17,nrisk19,nrisk23,nrisk25,nrisk28,nrisk29,nrisk30,nrisk31,nrisk32,nrisk33,nrisk35,nrisk36,nrisk37), 
              select(data,overallx,nrisk17,nrisk19,nrisk23,nrisk25,nrisk28,nrisk29,nrisk30,nrisk31,nrisk32,nrisk33,nrisk35,nrisk36,nrisk37), use = 'pairwise.complete.obs'), digits = 1)

colnames(highrelated) = c("Overall risk", "Victimization of other children (2)", "Mental/physical/emotional impairment (2)", " Substance abuse (2)", "History of domestic violence (2)", "Parenting skills/knowledge (1)", "Parenting skills/knowledge (2)", "Nurturance (1)","Nurturance (2)","Recognition of problem (1)", "Recognition of problem (2)","Protection of child (2)", "Cooperation (1)","Cooperation (2)")
rownames(highrelated) = c("Overall risk", "Victimization of other children (2)", "Mental/physical/emotional impairment (2)", " Substance abuse (2)", "History of domestic violence (2)", "Parenting skills/knowledge (1)", "Parenting skills/knowledge (2)", "Nurturance (1)","Nurturance (2)","Recognition of problem (1)", "Recognition of problem (2)","Protection of child (2)", "Cooperation (1)","Cooperation (2)")

corrplot(highrelated, method="shade", type="upper")
```









